Reproduce anaylses of Beninca et al (2008)

### 2016-02-19 code/report.Rmd
fixes

Check this against the data direct from Steve:
```{r}
from.steve <- read.csv(text=getURL(paste0(repo,"/data/original/interp_short_allsystem_newnames.csv")), header=T)
from.steve <- gather(from.steve, Species, Abundance, 2:13)
names(from.steve) <- c("Day.number", "variable", "value")
from.steve$value_steve <- from.steve$value 
from.steve <- select(from.steve, -value)

@@

## don't run this unless you have some time (it takes a while)
#LE <- Get_GLE_Beninca(X)
#save(LE, file="~/Desktop/GLE_estimate.Rdata")

>>>>

Check this against the data direct from Steve:
```{r}
from.steve <- read.csv(text=getURL(paste0(repo,"/data/original/interp_short_allsystem_original.csv")), header=T)
name_table <- read.csv(text=getURL(paste0(repo,"/data/reproduction/repro_steve_name_table.csv")), header=T)
names(from.steve) <- name_table$repro_names[match(names(from.steve), name_table$steve_names)]

from.steve <- gather(from.steve, Species, Abundance, 2:13)
names(from.steve) <- c("Day.number", "variable", "value")
from.steve$value_steve <- from.steve$value 
from.steve <- select(from.steve, -value)

@@

## To test the reproduction uncomment the next line of code
## don't run this unless you have some time (it takes a while)
#LE <- Get_GLE_Beninca(X)
#save(LE, file="~/Desktop/GLE_estimate.Rdata")
